### 2022-06-06 main/chapter_2ljets.tex
add parameter pull plot

Figure~\ref{fig:2ljets_summary_no_sr}
Figure~\ref{fig:2ljets_fit_corrmatrix}

@@

>>>>

Figure~\ref{fig:2ljets_summary_no_sr}
Figure~\ref{fig:2ljets_fit_corrmatrix}
Figure~\ref{fig:2ljets_fit_parameters}

@@

\begin{figure}[tp]
\centering
\includegraphics[height=0.9\textheight]{figures/2ljets_fit_parameters.pdf}
\caption[
Parameter values and errors from the background only-fit to control and signal
regions.
]{%
Parameter values and errors from the background only-fit to control and signal
regions.
Those named $\mu\_*$ are unconstrained normalization factors,
those named $\gamma\_*$ describe the combined statistical errors of simulated
samples,
and those named $\alpha\_*$ parametrize other variations.
The red arrow highlights the $\zjets$ generator comparison parameter
$\alpha\mathrm{\_Zjets\_alt}$ whose post-fit value is
% 1.8598e+00 +/-  6.87e-01
$1.86 \pm 0.69$;
since it exceeds $1.5$, it was otherwise excluded from this plot.
}
\label{fig:2ljets_fit_parameters}
\end{figure}
